<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-11-03 MainAnalysis.Rmd
Added DTXSID and got merge_model_fits working

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all("invivopkfit")
```

@@

@@

```{r, merge_pkfits, eval=FALSE}
all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
                                       "2compartment="=pk_output_2comp,
                                       "flat"=pk_output_flat),
                                        dtxsid.col = "DTXSID",
                                  species.col = "Species")

@@

### save data
paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".RData",sep="")
save(pk_output_1comp, file = paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
save(pk_output_2comp, file = paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
save(pk_output_flat, file = paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
save(raw_1comp, file = paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
save(raw_2comp, file = paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
save(raw_flat, file = paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))

save(pk_lombardo, file = paste("figures_rdata/pk_lombardo",THIS.DATE,".RData",sep=""))
```

@@

pk_all <- left_join(pk_data1, pk_lombardo, by = c("CAS" = "CAS #"))

@@

pk_all$`human CL (L/hr/kg)` <- pk_all$`human CL (mL/min/kg)` * 60 / 1000

pk_all$Vdist_norm <- abs(pk_all$Vdist / pk_all$`human VDss (L/kg)`)
pk_all$CLtot_norm <- abs(pk_all$CLtot / pk_all$`human CL (L/hr/kg)`)
pk_all$halflife_norm <- abs(pk_all$halflife / pk_all$`terminal  t1/2 (h)`)

>>>>

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all("invivopkfit")
# Clear memory:
rm(list=ls())
```

@@

pk_output_2comp$Vdist <- pk_output_2comp$V1*(pk_output_2comp$k12+pk_output_2comp$k21)/pk_output_2comp$k21

@@

```{r, merge_pkfits, eval=FALSE}
all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
                                       "2compartment"=pk_output_2comp,
                                       "flat"=pk_output_flat),
                                        dtxsid.col = "DTXSID",
                                  species.col = "Species")
```

@@

### save data
paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".RData",sep="")
save(pk_output_1comp, file = paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
save(pk_output_2comp, file = paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
save(pk_output_flat, file = paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
save(raw_1comp, file = paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
save(raw_2comp, file = paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
save(raw_flat, file = paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
save(all.fit.table, file = paste("figures_rdata/all_fit_table_",THIS.DATE,".RData",sep=""))
save(pk_lombardo, file = paste("figures_rdata/pk_lombardo",THIS.DATE,".RData",sep=""))
```

@@

pk_all <- left_join(all.fit.table, pk_lombardo, by = c("CAS" = "CAS #"))

@@

pk_all$`human CL (L/hr/kg)` <- pk_all$`human CL (mL/min/kg)` * 60 / 1000
pk_all$CLtot <- pk_all$Vdist*pk_all$kelim
pk_all$Vdist_norm <- abs(pk_all$Vdist / pk_all$`human VDss (L/kg)`)
pk_all$CLtot_norm <- abs(pk_all$CLtot / pk_all$`human CL (L/hr/kg)`)
pk_all$halflife_norm <- abs(pk_all$halflife / pk_all$`terminal  t1/2 (h)`)
